comgen-outline

### 2017-10-25 paper/comgen-paper.Rmd
finish restructuring generics case study

<!-- Consider how an uniformly underspecified threshold would interact with a uniformly uncertain belief about a probability (recall the thresholds defines what probabilities or states of the world should be ruled out).  -->
<!-- If the threshold is very high, only the highest probabilities would be left (i.e., pass the threshold). -->
<!-- If the threshold is slightly lower but still high, the highest probabilities would still pass the threshold, as would some that are slightly lower. -->
<!-- As the threshold takes on lower and lower values, more and more probabilities would surpass it. -->
<!-- When the threshold is very low, almost all probabilities are consistent with it. -->
<!-- But since we don't know *a priori* what the threshold is likely to be, each of theses situations is plausible. -->
<!-- The posterior distribution on probabilities or states of the world will favor higher probabilities (because they pass more thresholds), but will still include probabilities that are quite low [though they are *a posteriori* unlikely; see Figure \ref{fig:simluations} ].  -->
<!-- Speakers, thus, will produce generalizations with some probability in each state of the world, though the speaker will say the generalization more often when the propensities associated with the states of the world are higher [see Figure \ref{fig:simluations}]. -->

<!-- - Figure -->
  <!-- - Subfigure 1 [width = 0.2] (Uniform priors) [two rows, left subfigure] -->
  <!--   -- Basic L0 posteriors on degrees for uncertain, fixed at 0 and fixed at 0.5 -->
  <!--   -- Basic S1 posteriors on utterances, for prevalence 0 - 1 (and for fixed thresholds) -->
  <!-- - Subfigure 2 [width = 0.8] (L0 vs. L1 lifted vs. L1 unlifted x 4 priors x {speaker, listener} ) [model as color, lty; priors as columns x {speaker, listeners} as rows]  -->
  <!--   -- priors = [uniform, n-shaped, u-shaped, mixture model / maybe put more in appendix: rare, accidental, female, eggs] -->

<!--
mht: is it possible to construct priors in causals that would reflect the qualitative prediction shown here?
-->

<!-- $P(x)$ is a distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across animal categories.  -->
<!-- In Figure \ref{fig:schematic-unif}, are $L_1$ (Eq.~\ref{eq:L1}) posterior prevalence distributions on $x$ (red solid line) for several example prior prevalence distributions $P(x)$ (blue dashed line), as well as the $S_2$ generic endorsement probability for different levels of prevalence. -->
<!-- We name these example prior distributions to suggest properties that might be associated with such priors.  -->
<!-- (Later, we will empirically measure these priors for properties of interest.) -->
<!-- First, we explore generic interpretation and endorsement for priors of three different shapes (left column).  -->
<!-- For each of these, the $L_1$ posterior distribution (red solid) over prevalence is heavily driven by the prior (blue dashed). -->
<!-- $S_2$ endorsement probabilities for the generic (black solid) increase as a function of prevalence, and what counts as "true" (in terms of the prevalence) depends on the prior.  -->

<!-- \begin{figure} -->
<!-- \centering -->
<!--     \includegraphics[width=\columnwidth]{figs/schematics_s2.pdf} -->
<!--     \caption{Schematic prior distributions for prevalence $x$ (blue dashed), the pragmatic listener $L_1$ model's posterior distribution over prevalence upon hearing a generic utterance (red), and speaker $S_2$ model's endorsement of a generic utterance for different levels of prevalence (black). -->
<!--     The names given to these priors are meant to be suggestive of what kinds of properties these distributions might correspond to. -->
<!--     The left column uses prevalence priors modeled as Beta(15,15), Beta(4,1), and Beta(4,16) distributions. -->
<!--       The right column uses a prior distribution that is a mixture of the distribution to the left of it with a second component, modeled as Beta(0.5, 4.5), reflecting categories with 0\% property prevalence. -->
<!--     Horizontal dashed line at 0.5 is for convenience of comparing the point at which an utterance becomes judged as more true than false for $S_2$. -->
<!-- 	Note that the prior distribution over prevalence will be the same as $L_1$'s posterior distribution upon hearing the "null" utterance. -->
<!--     } -->
<!--   \label{fig:schematic-unif} -->
<!-- \end{figure} -->

<!-- To take one example, consider the distribution over what might be the property "are female" (top-left facet). -->
<!-- The \emph{a priori} prevalence is centered around 0.5. -->
<!-- Because of pragmatics, the pressure to be \emph{truthful} will drive likely threshold values below 0.5 (lower values are more likely to be true).  -->
<!-- At the same time, the pressure to be \emph{informative} will drive the threshold values up: Higher values are more likely to be informative.  -->
<!-- The result is a posterior over prevalence that is only marginally greater than the prior, making higher prevalence values more likely after hearing the generic.  -->
<!-- But the relative information gain is very little (the posterior is not very different from the prior), and thus the $S_2$ model is reluctant to endorse the generic unless the property is exceedingly prevalent.  -->
<!-- The same basic phenomenon can be observed for the other two example priors (left column): The posterior over prevalence heavily depends upon the prior, but is also not very different from the prior. -->

<!-- We now imagine what would happen if there were some kinds where the property was completely absent, while being present at some rate in other kinds. -->
<!-- Figure \ref{fig:schematic-unif} (right column) shows this possibility: mixing the distribution to the left of it with a second component at 0\% prevalence. -->
<!-- Consider the schematic prior over "lay eggs". -->
<!-- We see the pragmatic listener $L_1$'s posterior prevalence distribution is not very different from the interpretation that doesn't include the second component in the prior (here, "are female"), but it is dramatically different from the prior with two components (compare red with blue dashed line for the right column). -->
<!-- This suggests that when many categories have 0\% prevalence, lower thresholds are informative.  -->
<!-- Indeed, the $S_2$ model predicts that the generic becomes felicitous at lower prevalence levels (compare black line of left v. right column). -->
<!-- For "lay eggs", when the property is prevalent in 50\% of the kind (e.g., 50\% of birds lay eggs), endorsement of the generic (e.g., \emph{Birds lay eggs}) by the $S_2$ is roughly 0.85; for "are female", with the same prevalence (50\% of birds are female), endorsement for \emph{Birds are female} is only 0.50: It is judged to be neither true nor false.  -->
<!-- The important result is the asymmetry: the first generic can be endorsed more strongly than the second, at the same prevalence level; the exact endorsement rates depend on quantitative aspects of the priors, which must be determined empirically. -->

<!-- The model thus predicts differences in truth judgments depending on the prevalence prior.  -->
<!-- The first test of our theory, then, will be to see if these predictions correspond to human truth judgments of familiar generic sentences.  -->

<!-- Next is a hypothetical speaker, who reasons about the literal listener when deciding which utterance to produce. -->
<!-- \begin{eqnarray} -->
<!-- S_{1}(u \mid x, \theta) &\propto& \exp{(\lambda_1 \cdot \ln {L_{0}(x \mid u, \theta)} ) }\label{eq:S1} -->
<!-- \end{eqnarray} -->
<!-- This speaker $S_1$ also knows the threshold $\theta$ and chooses utterances to convey information to the literal listener $L_0$ . -->
<!-- Following RSA, this speaker is an approximately rational (speech-)actor with degree with rationality governed by parameter $\lambda_1$. -->

<!-- For the case of understanding a generic (e.g., *Dogs are friendly*), the relevant dimension for the adopted semantics is the prevalence of property within the category (e.g., the \% of dogs that are friendly). -->
<!-- In this model, a threshold $\theta$ is established in context by a Bayesian listener reasoning about what threshold would make this utterance true? -->

<!-- The model begins with a simple Bayesian agent---a literal listener---who updates her prior beliefs $P(x)$ according to the truth-functional meaning of the utterance heard $\denote{u}$. -->
<!-- \begin{eqnarray} -->
<!-- L_{0}(x \mid u, \theta) &\propto& {\delta_{\denote{u}(x, \theta)} \cdot P(x)} \label{eq:L0} -->
<!-- \end{eqnarray} -->
<!-- For the generic sentence, we assign the simplest possible meaning, a threshold on the prevalence: $\denote{u_{generic}} = P(F\mid K)>\theta$. -->

<!-- The likelihood $\delta_{\denote{u}(x)}$ is the Kronecker delta function returning $1$ for states $x$ compatible with utterance $u$ (i.e., where the prevalence $x$ is above the threshold $\theta$), and $0$ otherwise. -->
<!-- The literal listener is a hypothetical agent who knows the threshold $\theta$. -->

<!-- Next is a hypothetical speaker, who reasons about the literal listener when deciding which utterance to produce. -->
<!-- \begin{eqnarray} -->
<!-- S_{1}(u \mid x, \theta) &\propto& \exp{(\lambda_1 \cdot \ln {L_{0}(x \mid u, \theta)} ) }\label{eq:S1} -->
<!-- \end{eqnarray} -->
<!-- This speaker $S_1$ also knows the threshold $\theta$ and chooses utterances to convey information to the literal listener $L_0$ . -->
<!-- Following RSA, this speaker is an approximately rational (speech-)actor with degree with rationality governed by parameter $\lambda_1$. -->

<!-- For the generic sentence, we assign the simplest possible meaning, a threshold on the propensity: $\denote{u_{generic}} = P(F\mid K)>\theta$. -->
<!-- The prior distribution $P(h)$ is a distribution over likely degrees of propensity.  -->
<!-- For the case of understanding a generic (e.g., *Dogs are friendly*), the relevant dimension for the adopted semantics is the prevalence of property within the category (e.g., the \% of dogs that are friendly). -->

<!-- Life is only so long, however, and a person can only be in one place at a time. -->
<!-- The amount of data we can gather about any particular category, event, or causal force is extremely limited by these physical constraints. -->
<!-- Thus, it would be useful if language provided a simple way to communicate these generalizations to one another. -->

<!-- # A Formal Theory of Generalizations in Language -->

<!-- We find both the statistical and conceptual accounts compelling, but an important perspective is missing. -->
<!-- Linguistic generalizations are not unique in their flexibility. -->
<!-- Understanding language in general depends upon assumptions interlocutors make about each other and what content is under discussion.  -->
<!-- Viewing language understanding as a social reasoning process reveals that utterances carry a mosaic of interpretations with a complex sensitivity to context [@Clark1996; @Grice1975; @Levinson2000].  -->
<!-- Can the puzzles of generic language be understood as effects of pragmatic reasoning? -->
<!-- If so, we may be able to get away with a relatively simple, statistical,  semantic theory. -->
<!-- Abstract mental representations, then, may be the conceptual backdrop against which generic language is interpreted.  -->

<!-- We pursue such a line of inquiry, assuming the simplest truth-conditional meaning: a threshold on prevalence $P(F\mid K)>\theta$ [c.f., @Cohen1999]. -->
<!-- No fixed value of the threshold, $\theta$, would allow for the extreme flexibility generics exhibit (e.g. \emph{Mosquitos carry malaria}; \emph{Robins lay eggs} v. \emph{Robins are female}),  -->
<!-- so instead we allow this threshold to be established in context through pragmatic reasoning. -->
<!-- Such an inference would depend on background knowledge about properties and categories---potentially structured, conceptual knowledge. -->
<!-- This inference, nonetheless, is a general mechanism of understanding language, not specific to interpreting generic statements. -->
<!-- We formalize this hypothesis in the Rational Speech Act (RSA) theory---a formal, probabilistic theory of language understanding. -->
<!-- RSA is derived from social reasoning, formalized as recursive Bayesian inference between speaker and listener [@Frank2012; @Goodman2013; @Goodman2016; see also, @Franke2009; @Franke2015]. -->
<!-- @Goodman2016 provides a good introduction to the RSA framework and Appendix A presents a brief tutorial on RSA for the reader unfamiliar. -->

<!-- The model begins with a simple Bayesian agent---a literal listener---who updates her prior beliefs $P(x)$ according to the truth-functional meaning of the utterance heard $\denote{u}$. -->
<!-- \begin{eqnarray} -->
<!-- L_{0}(x \mid u, \theta) &\propto& {\delta_{\denote{u}(x, \theta)} \cdot P(x)} \label{eq:L0} -->
<!-- \end{eqnarray} -->
<!-- For the generic sentence, we assign the simplest possible meaning, a threshold on the prevalence: $\denote{u_{generic}} = P(F\mid K)>\theta$. -->
<!-- The prior distribution $P(x)$ is a distribution over likely states of the world.  -->
<!-- For the case of understanding a generic (e.g., *Dogs are friendly*), the relevant dimension for the adopted semantics is the prevalence of property within the category (e.g., the \% of dogs that are friendly). -->
<!-- The likelihood $\delta_{\denote{u}(x)}$ is the Kronecker delta function returning $1$ for states $x$ compatible with utterance $u$ (i.e., where the prevalence $x$ is above the threshold $\theta$), and $0$ otherwise. -->
<!-- The literal listener is a hypothetical agent who knows the threshold $\theta$. -->

<!-- To understand how language is interpreted pragmatically, we model a pragmatic listener $L_1$ who updates her prior beliefs $P(x)$ by reasoning about the generative process of the utterance, the speaker model $S_1$. -->
<!-- \begin{eqnarray} -->
<!-- L_{1}(x , \theta \mid u) &\propto& S_{1}(u \mid x, \theta) \cdot P(x) \cdot P(\theta) \label{eq:L1} -->
<!-- \end{eqnarray} -->
<!-- Following @Lassiter2013, we model the pragmatic listener as having uncertainty about the threshold: $P(\theta)$. -->
<!-- Though the listener doesn't know the threshold *a priori*, she resolves the threshold (i.e., the meaning) in context by integrating her prior beliefs $P(x)$ with the basic principles of communication to be truthful and informative, instantiated in her model of the speaker $S_1$ [@Lassiter2015; @GoodmanLassiter]. -->
<!-- In principle, thresholds could be learned over time for different contexts, but here we assume the listener has no informative knowledge about the semantic variable $P(\theta) = \text{Uniform([0, 1])}$. -->
<!-- The pragmatic listener $L_1$ (Eq. \ref{eq:L1}) is thus a model of *generic interpretation*: Upon hearing a generic, how should a listener update her beliefs? -->

@@

<!-- That is, "Mosquitos carry malaria" and "Robins lay eggs" are reasonable things to say, but "Robins are female" is not. -->
<!-- As a first test of our theory, we wish to explain the flexibility in endorsements of generics in terms of the relevant prior knowledge about properties, as explored through simulation in the **model simulations** section. -->
<!-- We validate these simulations empirically by measuring t and the referent-category feature-probability that the speaker model seeks to convey (the *referent feature-probability*) $h$ in Eq. \ref{eq:S1} (Expt. 1a). -->

<!-- <!-- The pragmatic speaker model $S_2$, Eq.~\ref{eq:S2}, is a model of truth judgments.  --> -->
<!-- We test our model on -->

<!-- To compare the model to empirical truth judgments, we measure the prior distribution over feature-probabilities of these properties (Expt. 1a). -->
<!-- We hypothesize that these prior distributions encode probabilities associated with conceptual distinctions [@Prasada2013]. -->
<!-- In particular, we hypothesize that different kind--property relations [e.g., *principled* v. *accidental relations*^[This is sometimes referred to as "statistical" relations.]; @Prasada2013] can be observed in the feature-probability prior.  -->
<!-- If, in fact, the feature-probability prior is a manifestation of deeper, conceptual knowledge, we would expect the feature-probability prior data to follow a multi-modal, mixture distribution where there exist qualitatively distinct modes or components to the prior, as probabilistic traces of the different types of kinds with respect to the property. -->
<!-- A prior that is structured would be one way in which our formal theory connects to other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007]. -->
<!-- As a simple test of this hypothesis---that the feature-probability prior encodes conceptual knowledge---we compare a structured (i.e., mixture) model of the prior data to an unstructured one. -->

<!-- After having validated a measure of the feature-probability prior, we consider the issue of primary theoretical interest: How well our *uncertain threshold* hypothesis accounts for endorsements of generic sentences (Expt. 1b). -->
<!-- In order to better understand the contribution of our theoretical framework, we evaluate alternative models that have either been previously analyzed in the generics literature or that are simpler forms of our *uncertain threshold* RSA model.  -->
## Experiment 1a: Generic endorsements

@@

Formally, we assume the prior data (analzyed independently for each property) was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
We model this distribution as a Beta distribuition that heavily favors probabilities near 0: $\text{Beta}(\gamma = 0.01, \delta = 100)$.^[
Note that we use the noncanonical mean $\gamma$ and concentration $\xi$ (or, inverse-variance) parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference. The shape parameterization can be recovered using: $\alpha = \gamma \cdot \xi; \beta = (1 - \gamma) \cdot \xi$.
]
The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\gamma, \xi)$.^[
Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; treating 1 as $1- \epsilon$ disproportionately influences the shape of $\mathcal{D}_{stable}$ relative to other responses.
This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
Similar results can be obtained by rounding 0 to 0.01. 
Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
]
Finally, we assume that these two components combine with mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \gamma = 0.01, \xi = 100) $$.

<!-- The unstructured alternative hypothesis assumes the data was generated by a single component in the prior distribution with unknown parameteres $P(d) = \text{Beta} (d \mid \gamma, \xi)$. -->

We put the following priors over the latent parameters of the model:

\begin{eqnarray}
\phi_i & \sim & \text{Uniform}(0, 1) \\
\gamma_i & \sim & \text{Uniform}(0, 1) \\
\xi_i & \sim & \text{Uniform}(0, 100) \\
\end{eqnarray}

where $i$ ranges over the different properties (e.g., *lays eggs*, *carries malaria*).

's data; however, we retain the imperfect simpler model for data-analytic ease going forward.

@@

Our underspecified-threshold endorsement model has access to the full prior distribution on feature-probabilities $P(h)$ (measured in Expt. 1b), from which the interpreter model infers likely thresholds for the generic. 
The endorsement model is a model of a speaker who is deciding whether or not to say the generic to the interpreter model.
We identify three, theoretically-substantial components of this model: (a) the prior distribution $P(h)$, (b) the endorsement deciding whether or not to produce the generic, and (c) the uncertain threshold.
As a control model, we use the same infrastructure but assign a fixed semantics to the utterance (i.e., analgous to the quantifier "some", which only rules out the lowest possible degree). 
This control model has both features (a) and (b) but lacks the uncertainty over the threshold (c).
This provides a strict test of our *simple but underspecified* hypothesis.

@@

### Referent feature-probability baseline

@@

### Cue validity and referent feature-probability

<!-- As a secondary alternative hypothesis, we explore whether prevalence and *cue validity* predicts generic endorsement of these items. -->
If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
*Cue validity* measures the salience of a category given a feature but also captures the distinctiveness of the feature. 
For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though it's role in generic meaning is controversial [@Leslie2007; @Leslie2008].

For a feature-probability distribution with a fixed set of categories, the cue validity of a kind given a feature can be calculated from the feature-probability prior distribution.
In empirical studies of generic language, however, it is often empirically measured [@Khemlani2012].
For this analysis, we measured cue validity using a free production paradigm, following @Cree2006.
Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity, see Appendix B.

@@

### Fixed threshold endorsement model

@@

The RSA model we propose for generic endorsement is a speaker model that decides whether or not to say the generic to a naive listener.
Unlike the simple regression models based on point-estimates of referent-category feature-probability and cue validity, this cognitive model has access to the full prior distribution on feature-probabilities $P(h)$.
This model has two other main architectural differences: an information-theoretic decision between producing the generic vs. an information-less alternative (formalized using RSA) and uncertainty about the semantic threshold that corresponds to the theoretical, core meaning of a generic statement.

We first test a model that has two of the the above three main architectural features.
This model has access to the full prior distribution on feature-probabilities as well as models an information-theoretic decision of producing the generic vs. an alternative.
The only difference is that this model uses a fixed-threshold to correspond to the core meaning of a generic statements.
For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).^[
Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria" would be literally false under this semantics).
]
This is a strong alternative model to our uncertain-threshold model; the only difference concerns the threshold.

<!-- Our pragmatic speaker model, $S_1$ in Eq. \ref{eq:S1}, reasons about whether it would be useful to say to the generic to this kind of listener so that the listener may acquire the same beliefs as the speaker (represented as the feature-probability of the property within the referent-category $h'$). -->
We use the empirically estimated referent-category feature-probability as the $h$ that the speaker $S_1$ is trying to communicate, and use the empirically measured priors from Expt. 1a as the listener's feature-probability prior $P(h)$.^[
Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
This corresponds to the more general form of the model described in a footnote in the model section. 
With these data, the predictions of these two models are nearly identical.
]
The $S_1$ model is then fully specified after setting the speaker optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).

To fit this model, we incorporate the RSA model into the Bayesian data analysis model of the feature-probability prior data (Expt. 1a) to create a single, joint-inference model where the speaker optimality parameter $\lambda_1$ is inferred jointly with the referent feature-probability $h_{k, f}$ for each category $k$ and property $f$ and the parameters of the feature-probability priors $P_f(h)$ for each property $f$ using data from Expt. 1a \& b (see Figure \ref{fig:genericsModelDiagram}).
For the parameters of the feature-probability distributions, we use the same priors described in Expt. 1a; for the speaker optimality parameter, we use a prior with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
We learn about the \emph{a posteriori} credible values of this joint inference model using an incrementalized-version of the  by collecting samples from 3 MCMC chains of 100,000 iterations removing the first 50,000 iterations for burn-in, using an incrementalized version of the Metropolis-Hastings algorithm [@Ritchie2016].

The posterior distribution of this joint inference model tells us what we should believe about the latent parameters of the model (referent feature-probabilities, feature-probability priors, and the single speaker optimality parameter) given the observed data, as well as what predictions the model makes given these parameter values.
Importantly, the model recapitulates the feature-probability prior data (e.g., the probability of laying eggs among various species) and the referent-category feature-probability data (e.g., the probability of laying eggs among robins; see Appendix A for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt. 1a).
This means the theoretically-interesting predictionso of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the details of the feature-probability distributions).

>>>>

@@

## Experiment 1a: Generic endorsements

@@

Formally, we assume the prior data (analzyed independently for each property) was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D}_{stable}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D}_{transient}$).
The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
We model this distribution as a Beta distribuition that heavily favors probabilities near 0: $\text{Beta}(\gamma = 0.01, \delta = 100)$.^[
Note that we use the noncanonical mean $\gamma$ and concentration $\xi$ (or, inverse-variance) parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference. The shape parameterization can be recovered using: $\alpha = \gamma \cdot \xi; \beta = (1 - \gamma) \cdot \xi$.
]
The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\gamma, \xi)$.^[
Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; treating 1 as $1- \epsilon$ disproportionately influences the shape of $\mathcal{D}_{stable}$ relative to other responses.
This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
Similar results can be obtained by rounding 0 to 0.01. 
Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
]
Finally, we assume that these two components combine with mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \gamma = 0.01, \xi = 100) $$.
<!-- The unstructured alternative hypothesis assumes the data was generated by a single component in the prior distribution with unknown parameteres $P(d) = \text{Beta} (d \mid \gamma, \xi)$. -->
We put the following priors over the latent parameters of the model:
\begin{eqnarray}
\phi_i & \sim & \text{Uniform}(0, 1) \\
\gamma_i & \sim & \text{Uniform}(0, 1) \\
\xi_i & \sim & \text{Uniform}(0, 100)
\end{eqnarray}
where $i$ ranges over the different properties (e.g., *lays eggs*, *carries malaria*).

@@

Our underspecified-threshold endorsement model has access to the full prior distribution on feature-probabilities $P(h)$ (measured in Expt. 1b), from which the interpreter model infers likely thresholds for the generic. 
The endorsement model is a model of a speaker who is deciding whether or not to say the generic to the interpreter model.
We identify three, theoretically-substantial components of this model: (a) the prior distribution $P(h)$, (b) the endorsement as a speaker decision of whether or not to produce the generic, and (c) the uncertain threshold.
As a control model, we use the same infrastructure but assign a fixed semantics to the utterance (i.e., analgous to the quantifier "some", which only rules out the lowest possible degree). 
This control model has both features (a) and (b) but lacks the uncertainty over the threshold (c).
This provides a strict test of the uncertain-threshold hypothesis.

@@

### Baseline models

#### Referent feature-probability

@@

#### Cue validity and referent feature-probability

##### Model specification

As a secondary baseline hypothesis, we explore whether prevalence and *cue validity* together predict generic endorsementse.
If feature-probability is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), *cue validity* is the inverse probability: $P(x \in k \mid x \in f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs).
*Cue validity* thus captures the distinctiveness of the feature for the category. 
For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria. 
Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though its role in generic meaning is controversial [@Leslie2007; @Leslie2008].
Empirically, cue validity is not a *necessary* criteron for generic endorsement (e.g., in the sentence: "Dogs have four legs").
Theoretically, if generics have to do with generalizations, which are formally described by the "forward probability", it is not obvious why the "inverse probability" (cue validity) would be part of the semantic content of generics.

We described in Expt 1b. that $P(h)$ can be decomposed into a prior on kinds $P(k)$ and the likelihood of a feature-probability given the kind $P(h \mid k)$.
If there is a finite number of kinds in the feature-probability prior for a feature, and one knows the probability of the feature for each kind (i.e., $P(h \mid k)= P(f \mid k)$), then the cue validity of that feature for a particular kind is encoded in the feature-probability prior and it can be derived via Bayes' Rule:
$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$
Previous empirical studies of generic language, however, have not measured the feature-probability prior and instead try to estimate cue-validity by asking about the distinctiveness of features for given animals [e.g., @Khemlani2012]
In keeping with this tradition, we measured cue validity using a free production paradigm, following @Cree2006.
Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?").
For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity as well as the *feature-probability prior derived cue validity*, see Appendix.

##### Results

@@

### Information-theoretic endorsement models

The model we propose for endorsing generalizations is a model of a speaker that decides whether or not to say the generalization to a naive listener.
Unlike the baseline regression models based on point-estimates of referent-category feature-probability and cue validity, this cognitive model has access to the full prior distribution on feature-probabilities $P(h)$.
This model has two other main architectural features: an information-theoretic decision between producing the generic vs. an information-less alternative (formalized in the speaker model) and uncertainty about the semantic threshold $P(\theta)$ that corresponds to the theoretical, core meaning of a generic statement.
We construct a strong, alternative model by removing the uncertainty about the semantic threshold $\theta$. 
We describe that model below in more detail; before, we describe our data analytic approach for this pair of models.

##### Model specification

For both fixed-threshold and uncertain-threshold models, the endorsement model $E$ (Eq. \ref{eq:S1}) decides whether or not to assert the generalization conditioned on a particular referent-category feature-probability $h'$^[
Rather than trying to communicate a particular $h$, the speaker could plausibly try to communicate her full belief distribution over $h$ to the listener. 
This corresponds to the more general form of the model described in a footnote in the model section. 
For these data, the predictions of these two models are nearly identical.
]
(e.g., given the percentage of robins that lay eggs, does it want to say "Robins lay eggs"?).
We use the empirically estimated referent-category feature-probability (the same as used in the baseline regression model) as the $h'$ in the endorser $E$ model.
The empirically measured priors from Expt. 1b are used as the literal interpreter's feature-probability prior $P(h)$.
The $E$ endorsement model is then fully specified (i.e., can generate predictions) after setting the optimality parameter $\lambda_1$ (in Eq. \ref{eq:S1}).

To fit this pair of endorsement models, we incorporate them into the Bayesian data analytic model of the feature-probability prior data (Expt. 1b) to create a single, joint-inference model where the optimality parameter $\lambda_1$ is inferred jointly with all the other latent parameters of the full model (the referent feature-probability $h'_{k, f}$ for each category $k$ and property $f$ and the parameters of the feature-probability priors $P_f(h)$ for each property $f$) using data from Expt. 1a \& b (see Figure \ref{fig:genericsModelDiagram}).
For the parameters of the feature-probability prior distributions, we use the same priors described in Expt. 1b; for the speaker optimality parameter, we use a prior with a range consistent with previous literature using the same model class: $\lambda_1 \sim \text{Uniform}(0,5)$.
We learn about the \emph{a posteriori} credible values of the joint inference models by collecting samples from 3 MCMC chains of 100,000 iterations removing the first 50,000 iterations for burn-in, using an incrementalized version of the Metropolis-Hastings algorithm [@Ritchie2016].

#### Fixed-threshold  model

We first test a model that has two of the the above three main architectural features.
This model has access to the full prior distribution on feature-probabilities as well as models an information-theoretic decision of producing the generic vs. an alternative.
The only difference is that this model uses a fixed-threshold to correspond to the core meaning of a generic statements.
For this model, we use $\theta = 0$ (corresponding intutively to the semantics of the quantified "Some" statements).^[
Other fixed-threshold models are possible (e.g., generic means "Most" $\theta = 0.5$) but require the further specification of a noise-model for participants' responses in the cases where participants endorse the statement when it is literally false (e.g., "Mosquitos carry malaria" would be literally false under a $\theta = 0.5$ semantics).
]
This is a strong alternative model to our uncertain-threshold model; the only difference concerns the threshold.

@@

The posterior distribution of this joint inference model tells us what we should believe about the latent parameters of the model (referent feature-probabilities, feature-probability priors, and the single speaker optimality parameter) given the observed data, as well as what predictions the model makes given these parameter values.
Importantly, the model recapitulates the same feature-probability prior data (e.g., the probability of laying eggs among various species) and the referent-category feature-probability data (e.g., the probability of laying eggs among robins; see Appendix for full posteriors) as it did when the Bayesian data analysis model only included these data and their associated model (results section of Expt. 1b).
This means the theoretically-interesting predictionso of this model --- predictions of generic endorsement --- are based on intuitively meaningful model components (i.e., the shapes of the feature-probability distributions).

We compare the fixed-threshold model's posterior predictive distribution of generic endorsement to the empirical truth judgments.
(Again the posterior predictive distribution marginalizes over the inferred parameter values to produce predictions about what the data \emph{should look like} given the endorsement model and the observed data.)
Figure \ref{fig:generic-endorsement-figure} (top right; top left subplot) shows the fixed-threshold model's ability to predict the generic endorsement data ($r^2(`r r2.gen.n`) = `r r2.gen.rsa.fixed`$; MSE = $`r mse.gen.rsa.fixed`$).
The model fails to distinguish any of the generic sentences because they are all somewhat true. 
All items get endorsed by at least some participants; the model then infers that the referent feature-probability $h'$ must be greater than 0\%; but, if the referent feature-probability is greater than 0\%, the statement is 100\% true given the fixed-threshold semantics.

The endorsement model decides if it better to assert the 0\%-threshold statement or stay silent. 
For some items, a fixed-threshold meaning carries some information-gain over silence (i.e., some model predictions \> 0.5). 
For many items, however, the 0\%-threshold is almost as meaning-less as silence; the model, thus, has a hard time strongly endorsing statements (most model predictions around 0.5\%).
Consistent with *a priori* intuition, assigning a fixed-semantics is too lenient a formalization for generic sentences. 
This demonstrates that the Bayesian data analytic approach used to fit the parameters of our model is not itself causally sufficient for any model of endorsements to explain the human endorsement data.
The fixed-threshold model, even with access to the full prior distribution $P(h)$, falls short in explaining the data.
